Paper One Summary

### 2015-09-01 paper/one/summary.tex
added scala and zonation definition

\section*{Important Keywords}
\begin{description}
\item [{Ecological~inference}] The idea that an observation or finding
at an aggregated level can apply at a disaggregated level. For example,
the idea that a model of defects at the package level also applies
at the file level
\item [{Ecological~fallacy}] An incorrect application of ecological inference.
For example, an instance where a model of defects at the product level
is incorrectly used to model defects at the file level
\end{description}

>>>>

\section*{Important Keywords}
\begin{description}
\item [{Ecological~inference}] The idea that an observation or finding
at an aggregated level can apply at a disaggregated level. For example,
the idea that a model of defects at the package level also applies.
at the file level
\item [{Ecological~fallacy}] An incorrect application of ecological inference. A discrepency between the findings at an aggregated level and disaggragated level.
For example, an instance where a model of defects at the product level
is incorrectly used to model defects at the file level.
\item [{Scale}] Size of an aggregated unit. THe larger the scale the bigger and fewer the aggregated units.
\item [{Zonation}] The manner in which aggregation is performed. For example, gerrymandering.
\end{description}
